Titlebot
=========

I string words together from the titles of scientific papers using Markov chains. Each word is sampled based on the probability that it follows the preceding word (i.e. I am a [bigram model](http://en.wikipedia.org/wiki/Bigram)).

So far, I have three Twitter accounts: 
* [@EcologyTitles](https://twitter.com/EcologyTitles)tweets about ecology
* [@ML_Titles](https://twitter.com/ML_Titles) tweets about machine learning.
* [@AnswersInMarkov](https://twitter.com/AnswersInMarkov) tweets about "creation science"

In general, the machine learning titles are harder to distinguish from real titles, but the ecology titles can be much funnier (see below).  Real "Creation science" is indistinguishable for Markov chain output.

The machine learning titles in the "data" folder were scraped by Philippe (@PhDP) from ArXiv and are available under a Creative Commons Share Alike license (some of them are CC-BY).

The ecology titles were scraped from PLOS journals using [rplos](https://github.com/ropensci/rplos). These titles are all CC-BY.

The Answers titles are copyrighted by Answers In Genesis. Their inclusion and transformation is not an infringement of copyright in the United States, however, as they are covered by the fair use doctrine. 

The code is available under The Artistic License 2.0 (see `LICENSE`).

The transition matrices are in a [standard format](http://math.nist.gov/MatrixMarket/formats.html#MMformat) as exported by `Matrix::writeMM`.

Praise for Titlebot:
====================

* "[This is exactly what I need to finish my PhD.](http://www.reddit.com/r/MachineLearning/comments/1ukbo5/tightening_mrf_relaxations_really_solve_sparse/cej8yel)

* "[an excellent example for why "no one has ever studied X" is not a sufficient reason to do a study!](https://twitter.com/duffy_ma/status/419629166787436546)"

* "[a good place to hunt for inspiring project ideas](https://twitter.com/noamross/status/419629657965617152)"

* "[That could be the title of the grant we just submitted](https://twitter.com/noamross/status/417781836626935808)"

* "[That sounds delicious](https://twitter.com/kara_woo/status/417781958476054528)"

* "[I actually would like to read this one. Would you mind writing it?](https://twitter.com/_NickGolding_/status/414848962164953088)"


Examples
========

```{r load_all, echo = FALSE, message = FALSE}
devtools::load_all()
set.seed(1)
```

### Machine learning:
```{r ML_example}
ML_bigram = load_bigram("StatMLTitles")
replicate(5, generate_title(bigram = ML_bigram))
```

### Ecology:
```{r ecology_example}
ecology_bigram = load_bigram("plos_ecology")
replicate(5, generate_title(bigram = ecology_bigram))
```

### Ecology:
```{r answers_example}
answers_bigram = load_bigram("Answers_Research_Journal")
replicate(5, generate_title(bigram = answers_bigram))
```